---
title: "Projects"
---

```{r}
#| message: false
#| warning: false
#| echo: false
library(tidyverse)
library(plotly)

steps <- read.csv("cyopersonaldata - Sheet1.csv")
```

# Data Analysis Project

This project was a personal research collection and visualization for ENVS 193DS course at UCSB. I collected data on my daily step count for six weeks, and compiled them into a visualization to see patterns in activity.

```{r}
stepsplot <- steps |> #calling in dataframe
  mutate(`day.of.week` = factor(`day.of.week`,#modifying the day of week column and converting day of week into a factor (categorical variable)
                                levels = c("M", "T", "W", "Th", "F", "Sa", "Su"), #specify levels
                                ordered = TRUE)) #keep in order

plot <- ggplot(steps, #calling in ggplot visualization and specifying dataset
       aes(x = `day.of.week`, #make x axis
           y = `steps.taken`, #make y axis
           fill = `day.of.week`))+ #fill in bar colors by day of the week
  stat_summary(fun = mean, #using the mean to summarize the y values
               geom = "bar")+ #making a bar chart
  labs(title = "Daily Step Count By Day of Week", #titling the graph
       x = "Day of Week", #labelling x axis
       y = "Steps Taken")+ #labelling y axis
  scale_fill_manual(values = c( #manually setting colors for each day of the week
    "M" = "red", #monday = red
    "T" = "orange", # tuesday = orange
    "W" = "yellow", #wednesday = yellow
    "Th" = "green", #thursday = green
    "F" = "blue", #friday = blue
    "Sa" = "violet", # saturday = purple
    "Su" = "hotpink" #sunday = pink
  ),
  drop = FALSE)+ #keep all the factors (days) in even if they have no data yet
  theme_minimal()+ #changin theme from the default
  theme(legend.position = "none") #removing legend

ggplotly(plot)

```

(insert affetive vizualization here!)

# Project #2: Conservation Plan

This was a conservation plan I helped put together for ENVS 137 - Conservation Planning. My group and I researched an endangered species (the Chinese Giant Salamander) , and created a comprehensive plan for their conservation and restoration.

Take a look here!

<iframe src="ENV S 137 CGS Conservaiton Plan.pdf" width="100%" height="900px">

</iframe>
